intro

### 2022-06-01 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
knitted document

# load libraries
library(here) # for path independent file referencing
# set top level directory to source file
here::i_am("flag_project_root_CERED.txt")

>>>>

# load libraries
library(here) # for path independent file referencing
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")
